Improved Smooth Free-Form Deformation with Sharp Feature Awareness

### 2016-09-06 paper.tex
修改以前抄大师的部分

\textcolor{green}{
}

@@

>>>>

\textcolor{green}{
    Traditional FFD deform the sampled vertices of the model as well as its extensions. Therefore, the quality of the deformation result depends on the sampling density of the vertex. To solve the sampling problem, adaptive upsampling approaches \cite{Gain99, Griessmair89, Parry86} are proposed which are more efficient than the naive uniform upsampling approach on CPU. However, they cannot handle certain special or pathological cases well. What's more, it is hard to be ported to GPU. Accurate FFD, proposed by Feng et al.~\cite{Feng98, Feng02, Feng00}, is another method to archive high quality of deformed model. But it is not efficient due to intensive computation and also comsumes considerable bandwidth. Thus, the algorithms are not interactive or performed in real time in pratical applications.
}

@@

\textcolor{green} {
    To obtain tremendous parallel computing power, lots of FFD implementations implemented via GPU. Chua et al. \cite{Chua00} proposed an OpenGL-oriented hardware evaluator sub-system specially designed for FFD evaluations. However, GPU parallel computing is developing in the opposite direction. GPU have evolved into general-purpose many-core processors. There're many implementations(\cite{Schein06}, \cite{Jung11}, \cite{Hahmann12}) accelerate FFD via GPGPU. The GPU acceleration component implemented by CUDA is 6.5-times faster thans its CPU counterpart.
}
